---
title: "model comparison"
output: html_document
---

```{r, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.width=4, fig.height=3,fig.align = "center",cache=TRUE)
library(ggplot2)
library(reshape)
library(grid)
library(dplyr)
library(gridExtra)
library(lme4)
library(reghelper)
library(RColorBrewer)
library(robustbase)
library(tidylog)
library(tidyr)
library(hash)
library(rstan)
library(png)
library(gtable)
library(hash)
library(purrr)
library(stringr)
#library(rjson)
library(ggforce)

paper_theme <- theme_light() + theme( axis.title.x = element_text(size=22),
                                      axis.text.x=element_text(
                                        size = 18), 
                                      axis.title.y = element_text(size = 22, vjust = 1),
                                      axis.text.y  = element_text(size = 18),
                             strip.text=element_text(size=16),
                                      axis.line.x = element_line(colour = "black"), 
                                      axis.line.y = element_line(colour = "black"),
                                      legend.title=element_text(size=20),
                                      legend.text=element_text(size=16),
                                      panel.grid.major=element_blank(),
                #   panel.background = element_rect(color = NA), 
                                      panel.grid.minor=element_blank())  


get_ll <- function(df) {
  logsumexp <- function(x) {
    max_x <- max(x)
    max_x + log(sum(exp(x - max_x)))
  }
  df <- df %>%
    group_by(tpt, seq_id) %>%
    mutate(norm = logsumexp(score)) %>%
    ungroup() %>%
    mutate(posterior = exp(score - norm)) 
  return(df)
}

preprocess_df_human <- function(df) {
  sm <- 1e-10
  df$attempt = 1
  df$id <- seq_len(nrow(df))
  df$n <- df$tpt
  df <- df[order(df$tpt),] %>%
      rename(pred_x = response_x, pred_y = response_y, func.name = seq_id, subj_id = subject_id) %>%
      group_by(subj_id, trial_idx, tpt) %>%
      mutate(r_id = subj_id) %>%
      mutate(true_dist=((true_x-prev_x)**2. + (true_y-prev_y)**2.)**0.5) %>%
      mutate(err_x=pred_x-true_x) %>%
      mutate(err_y=pred_y-true_y) %>%
      mutate(norm_err_x = err_x/(true_dist+sm)) %>%
      mutate(norm_err_y = err_y/(true_dist+sm)) %>%
      mutate(abs_err = ((err_x**2)+(err_y**2)) **0.5) %>%  
      mutate(norm_abs_err = abs_err/(true_dist)) %>%
      mutate(dist_from_prev = (((pred_x-true_x)**2)+((pred_y-true_y)**2)) **0.5) %>%
      ungroup() %>%
      mutate(scaled_err = scale(norm_abs_err)[,1])
  return(df)
}


preprocess_df_monkey <- function(df) {
  df$attempt = 1
  df$id <- seq_len(nrow(df))
  df <- df[order(df$n),] %>%
      rename(true_x=x_next, true_y=y_next, prev_x=x_curr, prev_y=y_curr, pred_x=x_pred, subj_id = monkey_name, pred_y=y_pred, func.name=func_id) %>%
      rename(tpt = n) %>%
      group_by(r_id, game_n, tpt) %>%
      mutate(true_dist=((true_x-prev_x)**2. + (true_y-prev_y)**2.)**0.5) %>%
      mutate(err_x=pred_x-true_x) %>%
      mutate(err_y=pred_y-true_y) %>%
      mutate(abs_err = ((err_x**2)+(err_y**2)) **0.5) %>%  
      mutate(norm_abs_err = abs_err/(true_dist)) %>%
      mutate(dist_from_prev = (((pred_x-true_x)**2)+((pred_y-true_y)**2)) **0.5) %>%
      ungroup() %>%
      mutate(tpt=tpt+1) %>%
      filter(tpt<15) %>%
      mutate(n=tpt)
  return(df)
}

preprocess_model <- function(df_model) {
  df_model$id <- seq.int(1,nrow(df_model))
  df_model <- df_model %>%
        get_ll() %>%
        rename(func.name = seq_id, n = tpt) %>%
        rowwise() %>%
        mutate(std_x = sd_x) %>%
        mutate(std_y = sd_y) %>%
        mutate(err_x = pred_x - true_x) %>%
        mutate(err_y = pred_y - true_y) %>%
        group_by(func.name) %>%
        filter(n > 0) %>%
        mutate(range_x = max(true_x) - min(true_x)) %>%
        mutate(range_y = max(true_y) - min(true_y)) %>%
        mutate(mean_x = mean(true_x)) %>%
        mutate(mean_y = mean(true_y)) %>%
        group_by(func.name, n) %>%
        ungroup() %>%
        group_by(func.name) %>%
        mutate(abs_err = ((true_x-pred_x)**2 + (true_y-pred_y)**2)**0.5) %>%
        mutate(mean_abs_err = mean(abs_err, na.rm=TRUE))
  return(df_model)
}

get_model_data <- function(df_model, s_id, t,  model_type) {
  s_id <- as.character(s_id[1])
  t <- t[1]
  df_use <- subset(df_model, (df_model$n==t) & (as.character(df_model$func.name) == as.character(s_id)))
    if (nrow(df_use) == 0) {
    return(NA) 
  } else {
    return(list(df_use$pred_x, df_use$std_x, df_use$pred_y, df_use$std_y, df_use$posterior, df_use$particle))
  }
}

add_new_columns_grouped <- function(df,df_model, func, group_cols, model_type, new_col_names) {
  # Number of times you want each row to be repeated
  n_particle <- length(unique(df_model$particle))
  # Create a new data frame by repeating each row
  df_expanded <- df %>% 
    slice(rep(1:n(), n_particle)) %>%
    group_by(id) %>%
    mutate(particle = rep(1:n_particle))
  df_expanded %>%
    group_by(across(all_of(group_cols))) %>%
    #summarize(result = list(func(!!sym(input_col))), .groups = 'drop') %>%
    summarize(result = list(func(df_model, func.name, n, model_type)), .groups = 'drop') %>%
    unnest_wider(result, names_sep = "_") %>%
    setNames(., c(group_cols, new_col_names)) %>%
    left_join(df, by = group_cols) 
}
```


###Load participant data
```{r}
df_adult <- preprocess_df_human(read.csv("data/participants/adults.csv"))
df_kid <- preprocess_df_human(read.csv("data/participants/kids.csv"))
df_monkey <- proprocess_df_monkey(read.csv("data/participants/monkeys_1.csv"))
```
# Load model paths
```{r}
gpnc_path <- 'data/models/gpnc.csv'
gpsl_path <- 'data/models/gpsl.csv'
ridge_path <- 'data/models/ridge.csv'
lot_path <- 'data/models/lot.csv'
lin_path <- 'data/models/linear.csv'
```


# Compute LL with params fit individually
```{r, message=FALSE}
compute_ll <- function(df_model, df_participant, out_path) {
  fn <- function(pars) { 
    o_sd <- pars[1]
    l_p <- pars[2]
    l_sd <- pars[3]
    df_result <- df_optim %>%
              filter(n > 2) %>%
              group_by(subj_id, func.name, r_id, n) %>%
              mutate(p_data_x =  dnorm(pred_x, mean=model_pred_x, sd=(model_std_x**2 + o_sd**2)**0.5)) %>%
              mutate(p_data_x = sm + (1-sm)*sum(model_posterior*p_data_x, na.rm=TRUE)) %>%
              mutate(p_data_y =  dnorm(pred_y, mean=model_pred_y, sd=(model_std_y**2+ o_sd**2)**0.5)) %>%
              mutate(p_data_y = sm + (1-sm)*sum(model_posterior*p_data_y, na.rm=TRUE)) %>%
              top_n(n=1,wt=model_particle) %>%
              mutate(p_data_x =(1-l_p)* p_data_x + l_p * dnorm(pred_x, mean=prev_x, sd=l_sd)) %>%
              mutate(p_data_y =(1-l_p)* p_data_y + l_p * dnorm(pred_y, mean=prev_y, sd=l_sd)) 
    ll <- sum(log(df_result$p_data_x), na.rm=TRUE) + sum(log(df_result$p_data_y), na.rm=TRUE) 
    return(-ll)
  }
  
df_participant_model <- add_new_columns_grouped(df_participant, df_model, get_model_data, c("func.name", "n"), "model", c("model_pred_x", "model_std_x", "model_pred_y", "model_std_y", "model_posterior", "model_particle")) %>%
                unnest(model_pred_x, model_pred_y, model_std_x, model_std_y, model_posterior, model_particle) %>%
                group_by(func.name) %>%
                mutate(min_x = mean(min_x, na.rm=T), min_y = mean(min_y, na.rm=T),
                       max_x = mean(max_x, na.rm=T), max_y = mean(max_y, na.rm=T)) %>%
                ungroup() %>%
                mutate(scale_by = (max_x-min_x)) %>%
                mutate(pred_x = (pred_x-min_x)/scale_by) %>%
                mutate(pred_y = (pred_y-min_y)/scale_by) %>%
                mutate(prev_x = (prev_x-min_x)/scale_by) %>%
                mutate(prev_y = (prev_y-min_y)/scale_by) %>%
                mutate(model_pred_x = (model_pred_x-min_x)/scale_by) %>%
                mutate(model_pred_y = (model_pred_y-min_y)/scale_by) %>%
                mutate(model_std_x = (model_std_x)/scale_by) %>%
                mutate(model_std_y = (model_std_y)/scale_by) %>%
                #mutate(acceptance_dist_x = acceptance_dist/scale_by,
                #       acceptance_dist_y = acceptance_dist/scale_by) %>%
                ungroup()
  
  
  #init param values
  other_noise <- 0.01
  lapse_p <- 0.5
  lapse_sd <- 0.2
  subj_param_dict = list()
  for(subj in unique(df_participant_model$subj_id)) {
    df_optim <- df_participant_model %>% filter(subj_id==subj)
    op_pars <- optim(c( other_noise, lapse_p, lapse_sd), fn,
          method = "L-BFGS-B",
          lower = c(1e-5, 0, 1e-5), upper = c(5,0.5, 5))
    pars <- op_pars$par
    subj_param_dict[[subj]] <- pars
  }
  sm <- 1e-10 
  
  df_result <- df_participant_model %>%
            mutate(o_sd = sapply(subj_id, function(x) unlist(subj_param_dict[[x]])[1])) %>%
            mutate(l_p = sapply(subj_id, function(x) unlist(subj_param_dict[[x]])[2])) %>%
            mutate(l_sd = sapply(subj_id, function(x) unlist(subj_param_dict[[x]])[3])) %>%
            filter(n > 2) %>%
            group_by(subj_id, func.name, n, r_id) %>%
            mutate(p_data_x =  dnorm(pred_x, mean=model_pred_x, sd=(model_std_x**2 + o_sd**2)**0.5)) %>%
            mutate(p_data_x = sm + (1-sm)*sum(model_posterior*p_data_x, na.rm=TRUE)) %>%
            mutate(p_data_y =  dnorm(pred_y, mean=model_pred_y, sd=(model_std_y**2+ o_sd**2)**0.5)) %>%
            mutate(p_data_y = sm + (1-sm)*sum(model_posterior*p_data_y, na.rm=TRUE)) %>%
            top_n(n=1,wt=model_particle) %>%
            mutate(p_data_x =(1-l_p)* p_data_x + l_p * dnorm(pred_x, mean=prev_x, sd=l_sd)) %>%
            mutate(p_data_y =(1-l_p)* p_data_y + l_p * dnorm(pred_y, mean=prev_y, sd=l_sd)) %>%
            mutate(LL = log(p_data_x) + log(p_data_y))
  
    ll <- sum(log(df_result$p_data_x), na.rm=TRUE) + sum(log(df_result$p_data_y), na.rm=TRUE)
    print(-ll)
    print(sum(df_result$LL))
  
  write.csv(df_result, out_path)
}
```


### Run model comparison
```{r, message=F}
model_paths = c(lot_path, gpnc_path, gpsl_path, lin_path, ridge_path)
models = c("lot", "gpnc", "gpsl", "lin", "ridge")
participants = c('adult', 'kid', 'monkey')
for (i in seq_along(models)) {
  model_name <- models[i]
  df_model <- preprocess_model(read.csv(model_paths[i]))
  for (j in seq_along(participants)) {
    if (participants[j] == 'adult') {
      df_participant <- df_adult
    } else if (participants[j] == 'kid') {
      df_participant <- df_kid
    } else if (participants[j] == 'monkey') {
      df_participant <- df_monkey
    } else {
      x = 1/0
    }
    print(model_name)
    print(participants[j])
    out_file <- paste("model_fits/LLs/", model_name, "_", participants[j], ".csv", sep="")
    compute_ll(df_model, df_human, out_file)
  }
}
```

# Compute LL individually under true and prev_pt models
```{r, echo=FALSE, message=FALSE}
# fn_random <- function(pars) { 
#   l_sd <- pars[1]
#   sm <- 1e-10 
#   df_result <- df_optim %>%
#             filter(n > 2) %>%
#             group_by(subj_id, func.name, n, r_id) %>%
#             top_n(n=1,wt=model_particle) %>%
#             mutate(p_data_x =  sm + (1-sm) * dnorm(pred_x, mean=prev_x, sd=l_sd)) %>%
#             mutate(p_data_y =  sm + (1-sm) * dnorm(pred_y, mean=prev_y, sd=l_sd))
#   ll <- sum(log(df_result$p_data_x), na.rm=TRUE) + sum(log(df_result$p_data_y), na.rm=TRUE) 
#   return(-ll)
# }
# 
# 
# lapse_sd <- 3
# kids_param_dict = list()
# for(subj in unique(df_human_model$subj_id)) {
#   df_optim <- df_human_model %>% filter(subj_id==subj)
#   op_pars <- optim(c(lapse_sd), fn_random,
#         method = "L-BFGS-B",
#         lower = c(0.1), upper = c(10))
#   pars <- op_pars$par
#   print(subj)
#   print(pars)
#   kids_param_dict[[subj]] <- pars
# }
# sm <- 1e-10
# 
# l_sd <- pars[1]
# df_result <- df_human_model %>%
#             mutate(l_sd = sapply(subj_id, function(x) unlist(kids_param_dict[[x]])[1])) %>%
#             filter(n > 2) %>%
#             group_by(subj_id, func.name, n, r_id) %>%
#             top_n(n=1,wt=model_particle) %>%
#             mutate(p_data_x = dnorm(pred_x, mean=prev_x, sd=l_sd)) %>%
#             mutate(p_data_y = dnorm(pred_y, mean=prev_y, sd=l_sd)) %>%
#             mutate(LL = log(p_data_x) + log(p_data_y))
# 
#   ll <- sum(log(df_result$p_data_x), na.rm=TRUE) + sum(log(df_result$p_data_y), na.rm=TRUE)
#   print(-ll)
#   print(sum(df_result$LL))
# 
# write.csv(df_result, 'model_fits/LLs/random_kid.csv')
# 
# fn_true <- function(pars) { 
#   l_sd <- pars[1]
#   sm <- 1e-10 
#   df_result <- df_optim %>%
#             filter(n > 2) %>%
#             group_by(subj_id, func.name, n, r_id) %>%
#             top_n(n=1,wt=model_particle) %>%
#             mutate(p_data_x = sm + (1-sm) * dnorm(pred_x, mean=true_x, sd=l_sd)) %>%
#             mutate(p_data_y =  sm + (1-sm) * dnorm(pred_y, mean=true_y, sd=l_sd))
#   ll <- sum(log(df_result$p_data_x), na.rm=TRUE) + sum(log(df_result$p_data_y), na.rm=TRUE) 
#   return(-ll)
# }
# 
# lapse_sd <- 3
# kids_param_dict = list()
# for(subj in unique(df_human_model$subj_id)) {
#   df_optim <- df_human_model %>% filter(subj_id==subj)
#   op_pars <- optim(c(lapse_sd), fn_true,
#         method = "L-BFGS-B",
#         lower = c(0.1), upper = c(10))
#   pars <- op_pars$par
#   print(subj)
#   print(pars)
#   kids_param_dict[[subj]] <- pars
# }
# sm <- 1e-10
# 
# 
# # add motor error and lapse prob?
# l_sd <- pars[1]
# df_result <- df_human_model %>%
#             mutate(l_sd = sapply(subj_id, function(x) unlist(kids_param_dict[[x]])[1])) %>%
#             filter(n > 2) %>%
#             group_by(subj_id, func.name, n, r_id) %>%
#             top_n(n=1,wt=model_particle) %>%
#             mutate(p_data_x = dnorm(pred_x, mean=true_x, sd=l_sd)) %>%
#             mutate(p_data_y = dnorm(pred_y, mean=true_y, sd=l_sd)) %>%
#             mutate(LL = log(p_data_x) + log(p_data_y))
# 
#   ll <- sum(log(df_result$p_data_x), na.rm=TRUE) + sum(log(df_result$p_data_y), na.rm=TRUE)
#   print(-ll)
#   print(sum(df_result$LL))
# 
# write.csv(df_result, 'model_fits/LLs/true_kid.csv')
```


# Analyze model fits
```{r}
path <- "model_fits/LLs/"

lot_kid <- read.csv(paste(path, "lot_kid.csv", sep=""))
gpsl_kid <- read.csv(paste(path, "gpsl_kid.csv", sep=""))
gpnc_kid <- read.csv(paste(path, "gpnc_kid.csv", sep=""))
ridge_kid <- read.csv(paste(path, "ridge_kid.csv", sep=""))
lin_kid <- read.csv(paste(path, "lin_kid.csv", sep=""))
#rand_kid <- read.csv(paste(path, "random_kid.csv", sep=""))
#true_kid <- read.csv(paste(path, "true_kid.csv", sep=""))

lot_adult <- read.csv(paste(path, "lot_adult.csv", sep=""))
gpsl_adult <- read.csv(paste(path, "gpsl_adult.csv", sep=""))
gpnc_adult <- read.csv(paste(path, "gpnc_adult.csv", sep="")))
ridge_adult <- read.csv(paste(path, "ridge_adult.csv", sep=""))
lin_adult <- read.csv(paste(path, "lin_adult.csv", sep=""))
#rand_adult <- read.csv(paste(path, "random_adult.csv", sep=""))
#true_adult <- read.csv(paste(path, "true_adult.csv", sep=""))

lot_monkey <- read.csv(paste(path, "lot_monkey.csv", sep=""))
gpsl_monkey <- read.csv(paste(path, "gpsl_monkey.csv", sep=""))
gpnc_monkey <- read.csv(paste(path, "gpnc_monkey.csv", sep=""))
ridge_monkey <- read.csv(paste(path, "ridge_monkey.csv", sep=""))
lin_monkey <- read.csv(paste(path, "lin_monkey.csv", sep=""))
#rand_monkey <- read.csv(paste(path, "random_monkey.csv", sep=""))
#true_monkey <- read.csv(paste(path, "true_monkey.csv", sep=""))

```


# Stats
```{r, message=F}
get_AIC <- function(all_fits) {
  grouped <- all_fits %>%
                  group_by(model) %>%
                  mutate(model_sum_LL = sum(LL, na.rm=T)) %>%
                  group_by(subj_id, model, func.name) %>%
                  summarize(LL_mean = mean(LL, na.rm = TRUE),
                            model_sum_LL = mean(model_sum_LL), o_sd = mean(o_sd),
                            l_sd = mean(l_sd), l_p = mean(l_p)) %>%
                  ungroup() %>%
                  group_by(subj_id, model) %>%
                  summarize(LL_mean = mean(LL_mean, na.rm=TRUE),
                            model_sum_LL = mean(model_sum_LL), o_sd = mean(o_sd),
                            l_sd = mean(l_sd), l_p = mean(l_p)) %>%
                  ungroup() %>%
                  group_by(model) %>%
                  mutate(LL_mean_model = mean(LL_mean),
                         model_sum_LL = mean(model_sum_LL), o_sd_mean = mean(o_sd),
                         l_sd_mean = mean(l_sd), l_p_mean = mean(l_p))
  
  n_subjs = length(unique(grouped$subj_id))
  
  top <- grouped %>%
         group_by(subj_id) %>%
         slice_max(order_by = LL_mean) %>%
         ungroup()
  
  print(table(top$model))
  
  df_aic <- grouped %>%
            group_by(model) %>%
            summarize(LL_mean_model=mean(LL_mean_model),
                      model_sum_LL=mean(model_sum_LL), o_sd_mean=mean(o_sd_mean),
                      l_sd_mean=mean(l_sd_mean), l_p_mean=mean(l_p_mean)) %>%
            group_by(model) %>%
            mutate(n_params = ifelse(model%in%c("Prev pt", "True pt"), n_subjs, n_subjs*3)) %>%
            mutate(AIC = (2*n_params) - (2*model_sum_LL)) %>%
            ungroup() %>%
            mutate(delta_AIC = AIC - min(AIC))

  return(df_aic)
}

all_fits_adult <- bind_rows(lot_adult %>%mutate(model="LoT"),
                           gpnc_adult%>%mutate(model="GPNC"),
                           gpsl_adult%>%mutate(model="GPSL"),
                           ridge_adult%>%mutate(model="Ridge"),
                           lin_adult%>%mutate(model="Lin."))

all_fits_kid <- bind_rows(lot_kid%>%mutate(model="LoT"),
                         gpnc_kid%>%mutate(model="GPNC"),
                         gpsl_kid%>%mutate(model="GPSL"),
                         ridge_kid%>%mutate(model="Ridge"),
                         lin_kid%>%mutate(model="Lin."))


all_fits_monkey <- bind_rows(lot_monkey%>%mutate(model="LoT"),
                            gpsl_monkey%>%mutate(model="GPSL"),
                            gpnc_monkey%>%mutate(model="GPNC"),
                            ridge_monkey%>%mutate(model="Ridge"),
                            lin_monkey%>%mutate(model="Lin."))

print("Adults bet fit:")
df_aic_adult <- get_AIC(all_fits_adult)
print("Kids best fit:")
df_aic_kid <- get_AIC(all_fits_kid)
print("Monkeys best fit:")
df_aic_monkey <- get_AIC(all_fits_monkey)


```


```{r}
grouped_kid <- all_fits_kid %>%
                  group_by(model) %>%
                  mutate(model_sum_LL = sum(LL, na.rm=T)) %>%
                  group_by(subj_id, model, func.name) %>%
                  summarize(LL_mean = mean(LL, na.rm = TRUE),
                            model_sum_LL = mean(model_sum_LL), o_sd = mean(o_sd),
                            l_sd = mean(l_sd), l_p = mean(l_p)) %>%
                  ungroup() %>%
                  group_by(subj_id, model) %>%
                  summarize(LL_mean = mean(LL_mean, na.rm=TRUE),
                            model_sum_LL = mean(model_sum_LL), o_sd = mean(o_sd),
                            l_sd = mean(l_sd), l_p = mean(l_p)) %>%
                  ungroup() %>%
                  group_by(model) %>%
                  mutate(LL_mean_model = mean(LL_mean),
                         model_sum_LL = mean(model_sum_LL), o_sd_mean = mean(o_sd),
                         l_sd_mean = mean(l_sd), l_p_mean = mean(l_p))
  
n_subjs = length(unique(grouped_kid$subj_id))
  
top <- grouped_kid %>%
    group_by(subj_id) %>%
    slice_max(order_by = LL_mean) %>%
    ungroup()
mean(top$o_sd)
mean(top$l_sd)
```

```

```{r}
grouped_adult <- all_fits_adult %>%
                  group_by(model) %>%
                  mutate(model_sum_LL = sum(LL, na.rm=T)) %>%
                  group_by(subj_id, model, func.name) %>%
                  summarize(LL_mean = mean(LL, na.rm = TRUE),
                            model_sum_LL = mean(model_sum_LL), o_sd = mean(o_sd),
                            l_sd = mean(l_sd), l_p = mean(l_p)) %>%
                  ungroup() %>%
                  group_by(subj_id, model) %>%
                  summarize(LL_mean = mean(LL_mean, na.rm=TRUE),
                            model_sum_LL = mean(model_sum_LL), o_sd = mean(o_sd),
                            l_sd = mean(l_sd), l_p = mean(l_p)) %>%
                  ungroup() %>%
                  group_by(model) %>%
                  mutate(LL_mean_model = mean(LL_mean),
                         model_sum_LL = mean(model_sum_LL), o_sd_mean = mean(o_sd),
                         l_sd_mean = mean(l_sd), l_p_mean = mean(l_p))
  
n_subjs = length(unique(grouped_adult$subj_id))
  
top <- grouped_adults %>%
    group_by(subj_id) %>%
    slice_max(order_by = LL_mean) %>%
    ungroup()
print(table(top$model))
```

