---
title: "Main accuracy-based analyses"
output: html_document
---

```{r, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.width=4, fig.height=3,fig.align = "center",cache=TRUE)
library(ggplot2)
library(reshape)
library(grid)
library(dplyr)
library(gridExtra)
library(lme4)
library(reghelper)
library(RColorBrewer)
library(robustbase)
library(tidylog)
library(brms)
library(tidyr)
library(hash)
library(rstan)
library(png)
library(gtable)
library(ggimage)
library(hash)
library(purrr)
library(stringr)
library(ggforce)

paper_theme <- theme_light() + theme(
  axis.text.x=element_text(colour="#292929", size = 14), 
  axis.title.x = element_text(size=18, family="Georgia"),
  axis.title.y = element_text(size = 18, vjust = 1,  family="Georgia"),
  axis.text.y  = element_text(size = 14, colour="#292929", family="Georgia"),
  strip.text=element_text(size=16,color="black", family="Georgia"),
  strip.background = element_rect(colour = "grey50", fill = "white"),
  panel.background = element_rect(fill = "white", colour = "grey50"),
  axis.ticks.x=element_blank(),axis.ticks.y=element_blank(),
  axis.line.x = element_line(colour = "black"), 
  axis.line.y = element_line(colour = "black"),
  legend.title=element_text(size=18, family="Georgia"),
  legend.text=element_text(size=15, family="Georgia"),
  panel.grid.major = element_blank(), panel.grid.minor = element_blank())

sm <- 1e-10

preprocess_df_adult <- function(df) {
  df <- df[order(df$tpt),] %>%
        rename(pred_x = response_x, pred_y = response_y, func.name = seq_id, subj_id = subject_id) %>%
        group_by(subj_id, trial_idx, tpt) %>%
        mutate(true_dist=((true_x-prev_x)**2. + (true_y-prev_y)**2.)**0.5) %>%
        mutate(err_x=pred_x-true_x) %>%
        mutate(err_y=pred_y-true_y) %>%
        mutate(norm_err_x = err_x/(true_dist+sm)) %>%
        mutate(norm_err_y = err_y/(true_dist+sm)) %>%
        mutate(abs_err = ((err_x**2)+(err_y**2)) **0.5) %>%  
        mutate(abs_rel_err = abs_err/(true_dist)) %>%
        mutate(dist_from_prev = (((pred_x-true_x)**2)+((pred_y-true_y)**2)) **0.5) %>%
        ungroup() %>%
        mutate(scaled_err = scale(abs_rel_err)[,1])
  return(df)
}

preprocess_df_children <- function(df) {
  df_kid <- df[order(df$tpt),] %>%
        rename(pred_x = response_x, pred_y = response_y, func.name = seq_id, subj_id = subject_id) %>%
        group_by(subj_id, trial_idx, tpt) %>%
        mutate(true_dist=((true_x-prev_x)**2. + (true_y-prev_y)**2.)**0.5) %>%
        mutate(err_x=pred_x-true_x) %>%
        mutate(err_y=pred_y-true_y) %>%
        mutate(norm_err_x = err_x/(true_dist+sm)) %>%
        mutate(norm_err_y = err_y/(true_dist+sm)) %>%
        mutate(abs_err = ((err_x**2)+(err_y**2)) **0.5) %>%  
        mutate(abs_rel_err = abs_err/(true_dist)) %>%
        mutate(dist_from_prev = (((pred_x-true_x)**2)+((pred_y-true_y)**2)) **0.5) %>%
        ungroup() %>%
        mutate(scaled_err = scale(abs_rel_err)[,1])
  
  # Update session numbers so that activity < 1 hr apart is recorded as a single session
  df_kid <- df_kid %>%
            group_by(subj_id) %>%
            mutate(session = session-min(session)+1) %>%
            mutate(n_sessions = max(session)) %>%
            ungroup()

  time_bt_sessions <- df_kid %>%
                      distinct(subj_id, session, start_time) %>%
                      group_by(subj_id) %>%
                      mutate(time_bt_first_and_last_session = max(start_time)-min(start_time)) %>%
                      arrange(subj_id, session) %>%
                      mutate(time_since_last_session = start_time - lag(start_time)) %>%
                      ungroup() %>%
                      select(-c("start_time"))
  
  df_kid <- df_kid %>%
            merge(time_bt_sessions, by=c("subj_id", "session"))
         
  session_offsets <- df_kid %>%
                      group_by(subj_id, session) %>%
                      summarize(trials_per_session = max(trial_idx), .groups = "drop") %>%
                      arrange(subj_id, session) %>%
                      group_by(subj_id) %>%
                      mutate(trials_in_prev_session = lag(trials_per_session, default = 0)) %>%
                      mutate(trials_before_session = lag(cumsum(trials_per_session), default = 0)) 
  
  df_kid <- df_kid %>%
         merge(session_offsets, by = c("subj_id", "session")) %>%
         mutate(trial_idx_across_sessions = trial_idx + trials_before_session)
  
  # if less than 1 hour between sessions, count it as a single session
  min_time_between_sessions = 1/24
  df_kid <- df_kid %>%
            mutate(session = ifelse((session>1) & (time_since_last_session<min_time_between_sessions),
                                    session - 1,
                                    session),
                trial_idx = ifelse((session>1) & (time_since_last_session<min_time_between_sessions),
                                   trial_idx + trials_in_prev_session,
                                   trial_idx)) %>%
        group_by(subj_id) %>%
        mutate(n_sessions = max(session)) %>%
        group_by(subj_id, session) %>%
        mutate(trials_per_session = max(trial_idx)) %>%
        ungroup() %>%
        group_by(subj_id) %>%
        mutate(n_trials_total = max(trial_idx_across_sessions)) %>%
        group_by(subj_id, session, tpt) %>%
        mutate(trial_1_time_since_start = ifelse(trial_idx==1, trial_time_since_start, NA),
               trial_1_time_since_start = mean(trial_1_time_since_start, na.rm=T),
               trial_duration_sum = sum(trial_duration),
               session_duration = trial_1_time_since_start + trial_duration_sum) %>%
        ungroup() %>%
        select(-c(trial_1_time_since_start, trial_duration_sum, start_time, time_since_last_session, trials_before_session, trials_in_prev_session))
}


preprocess_df_monkey <- function(df) {
  df <- df %>%
        rename(tpt = n)
  
  df <- df[order(df$tpt),] %>%
        rename(true_x=x_next, true_y=y_next, prev_x=x_curr, prev_y=y_curr, pred_x=x_pred,
               subj_id = monkey_name, pred_y = y_pred, func.name = func_id) %>%
        group_by(r_id, game_n, tpt) %>%
        mutate(true_dist=((true_x-prev_x)**2. + (true_y-prev_y)**2.)**0.5) %>%
        mutate(err_x=pred_x-true_x) %>%
        mutate(err_y=pred_y-true_y) %>%
        mutate(abs_err = ((err_x**2)+(err_y**2)) **0.5) %>%  
        mutate(abs_rel_err = abs_err/(true_dist)) %>%
        mutate(dist_from_prev = (((pred_x-true_x)**2)+((pred_y-true_y)**2)) **0.5) %>%
        mutate(r_id = as.character(r_id)) %>%
        ungroup()
  return(df)
}

add_rank_time_column <- function(dataframe) {
  # Convert 'time' column to a date format, ignoring the clock time information
  dataframe$date <- as.Date(dataframe$Current_time, format = "%a %b %d %H:%M:%S %Y")
    unique_dates <- dataframe %>%
    distinct(date) %>%
    arrange(date) %>%
    mutate(rank_time = row_number())
  
  h <- hash()
  for (i in 1:nrow(unique_dates)) {
    date <- unique_dates$date[i]
    rank_time <- unique_dates$rank_time[i]
    h[date] = rank_time
  }

  dataframe <- dataframe %>%
                rowwise() %>%
                mutate(ranked_day = h[[as.character(date)]])
  
  return(dataframe)
}


capitalize_words <- function(s) {
  words <- str_split(s, " ")[[1]]
  words <- ifelse(words == "to", "to", str_to_title(words))
  paste(words, collapse = " ")
}

data_dir <- "data/"
preprocessed_data_dir <- "preprocessed_data/"
fig_dir <- "figs/"
```

# Plot stimuli
```{r}
df_stim <- read.csv(paste0(data_dir, "models/lot.csv")) %>%
           distinct(tpt, true_x, true_y, seq_id)
lims <- df_stim %>%
  group_by(seq_id) %>%
  summarize(xmin = min(true_x),
            xmax = max(true_x),
            ymin = min(true_y),
            ymax = max(true_y),
            .groups = "drop") %>%
  rowwise() %>%
  mutate(xrange = xmax - xmin,
        yrange = ymax - ymin,
        maxrange = max(xrange, yrange),
        xmid = (xmin + xmax)/2,
        ymid = (ymin + ymax)/2,
        xmin = xmid - maxrange/2,
        xmax = xmid + maxrange/2,
        ymin = ymid - maxrange/2,
        ymax = ymid + maxrange/2)

plot_func <- function(f, lw) {
  lim <- lims %>% filter(seq_id == f)
  ggplot(df_stim %>% filter(seq_id == f)) +
    geom_path(aes(x = true_x, y = true_y), linetype = "dotted") +
    geom_point(aes(x = true_x, y = true_y, alpha = tpt)) +
    paper_theme +
    theme(axis.text.x  = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y  = element_blank(),
          axis.line.x  = element_blank(), 
          axis.line.y  = element_blank(), 
          panel.border = element_rect(linewidth=lw, color="black"),
          strip.text = element_blank()) +
    coord_fixed(xlim = c(lim$xmin, lim$xmax),
                ylim = c(lim$ymin, lim$ymax),
                ratio = 1) +
    guides(alpha = "none")
}

plots <- list()
func_order <- c("line", "stairs", "stairs_2", "square_spiral", "alternating_diff_2", "square_2", "alternating_diff_1", "123",
                "radial_1", "zigzag_widening", "hourglass_1", "zigzag_1", "3_pts", "sine", "plus", "decreasing_y",
                "triangle_1", "increasing_lines", "zigzag_3", "f_curly_2", "spiral_outward", "zigzag_2", "hexagon", "radial_increasing")
i=0
for (f in func_order) {
  i=i+1
  if (i%%8==0) {
    lw = 1
  } else {
    lw= 0.1
  }
  plots[[length(plots) + 1]] <- plot_func(f, lw) + theme(plot.margin = margin(0.01, 0.01, 0.01, 0.01, "in"))
}

p <- grid.arrange(grobs=plots, nrow=3)


```


# Monkey training, preprocessing
```{r}

df_monkey_train <- preprocess_df_monkey(read.csv("data/participants/monkeys_train.csv"))

df_monkey_train$id <- seq.int(1,nrow(df_monkey_train))
df_monkey_train <- add_rank_time_column(df_monkey_train)

ranked_days <- df_monkey_train %>%
  group_by(subj_id) %>%
  distinct(ranked_day) %>%
  arrange(ranked_day) %>%
  mutate(rank_day = row_number()) %>%
  ungroup()

unique_sequences_df <- df_monkey_train %>%
  group_by(func.name, tpt) %>%
  top_n(n = 1, wt = id) %>%
  select(func.name, tpt, true_x, true_y) %>%
  ungroup()

df_monkey_train <- df_monkey_train %>%
  left_join(unique_sequences_df, by = c("func.name", "tpt")) %>%
    left_join(ranked_days, by = c("subj_id", "ranked_day")) %>%
    rowwise() %>%
    mutate(func.type = gsub("\\.\\d+$", "", func.name)) %>%
      mutate(correct_120 = ifelse(dist_from_true < 120, 1, 0)) %>%

      rowwise() %>%
      mutate(func.type = gsub("\\.\\d+$", "", func.name),
                  t_id = paste(r_id, func.name, game_n)) %>%
    group_by(subj_id) %>%
    mutate(rank_day = rank_day - min(rank_day)+1) %>%
    filter((guess_number <= 10) | is.na(guess_number)) %>%
    group_by(func.type) %>%
    mutate(min_rank_day = min(rank_day)) %>%
    ungroup() %>%
    arrange(min_rank_day) %>%
    mutate(func.type = factor(func.type, levels = unique(func.type))) %>%
    arrange(rank_day, game_n, tpt) %>%
    group_by(subj_id, func.type) %>%
    mutate(func_examples = cumsum(!duplicated(t_id))) 


```

# Monkey accuracy analyses
```{r}
pattern_accuracy <- df_monkey_train %>%
  filter(attempt_number == 1) %>%
  group_by(subj_id, func.type) %>%
  summarise(
    n_trials = n(),
    mean_accuracy_120 = mean(correct_120, na.rm = TRUE),
    mean_distance_error = mean(dist_from_true, na.rm = TRUE),
    final_accuracy = mean(correct_120[func_examples >= quantile(func_examples, 0.8)], na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  arrange(subj_id, desc(mean_accuracy_120))

cat("ACCURACY BY PATTERN TYPE\n")
cat("========================\n")
for(monkey_name in c("Monkey 1", "Monkey 2")) {
  cat(sprintf("\n%s (sorted by 120px accuracy):\n", monkey_name))
  cat("Pattern Type                | Trials | 120px Acc | Final Acc | Mean Error\n")
  cat("---------------------------|--------|-----------|-----------|----------\n")
  
  monkey_data <- pattern_accuracy %>% filter(subj_id == monkey_name)
  for(i in 1:nrow(monkey_data)) {
    pattern <- gsub("_", " ", monkey_data$func.type[i])
    pattern <- str_to_title(pattern)
    cat(sprintf("%-26s | %6d | %7.1f%% | %8.1f%% | %7.1f px\n",
                pattern,
                monkey_data$n_trials[i],
                monkey_data$mean_accuracy_120[i] * 100,
                monkey_data$final_accuracy[i] * 100,
                monkey_data$mean_distance_error[i]))
  }
}

```


# Monkey training, accuracy over time plot
```{r, fig.width=10, fig.height=6}

df_monkey_train$scaled_func_examples <- floor(df_monkey_train$func_examples/15)*15
xmin <- min(df_monkey_train$scaled_func_examples)
xmax <- max(df_monkey_train$scaled_func_examples)
xscale <- xmax - xmin

pretty_label <- function(x) sapply(gsub("_", " ", x), capitalize_words)

ggplot(data=df_monkey_train %>% filter(attempt_number == 1), aes(x=scaled_func_examples, y=correct_120, group=subj_id, color=subj_id)) +

        stat_summary(fun="mean", geom="line", size=0.5, alpha=0.9) +
        stat_summary(fun="mean", geom="point", size=1) +
        stat_summary(fun="mean", geom="point", color="white", size=0.25) +
        stat_summary(fun.data="mean_se", geom="errorbar", width=1) +
        scale_color_manual(values = c("dodgerblue", "orange"), labels=c("Monkey 1", "Monkey 2")) +
        scale_x_continuous(breaks=c(0,100, 200)) +
        scale_y_continuous(breaks=c(0,0.5,1)) +
        guides(alpha="none", color="none") +
        coord_cartesian(xlim=c(xmin, xmax+10), ylim=c(0,1.08)) +
        facet_wrap(~func.type, nrow=4, labeller = labeller(func.type = pretty_label)) +
        paper_theme +
        labs(x="Pattern example number", y="Accuracy" ) +
        
        paper_theme+ theme(legend.title = element_blank(),
                     strip.background = element_blank(),
                     strip.text = element_text(size=12)) 

```

# Load participant data for test sequences
```{r}
df_adult <- preprocess_df_adult(read.csv(paste0(data_dir, "participants/adults.csv"))) %>% filter(tpt>2) %>% mutate(agent="Adults")
df_kid <- preprocess_df_children(read.csv(paste0(data_dir, "participants/kids.csv"))) %>% filter(tpt>2) %>% mutate(agent="Kids")
df_monkey_test <- preprocess_df_monkey(read.csv(paste0(data_dir,  "participants/monkeys.csv"))) %>% filter(tpt>2) %>% mutate(agent="Monkeys")


df_all <- bind_rows(df_adult, df_monkey_test, df_kid)
```

# Compute overall and final timepoint accuracy by agent 
```{r}
mean_df <- df_all %>%
           group_by(agent, func.name, tpt, subj_id) %>%
           summarize(accuracy=mean(correct, na.rm=T), .groups="drop") %>%
           group_by(agent, func.name, tpt) %>%
           summarize(accuracy=mean(accuracy, na.rm=T))

print(mean_df %>% group_by(agent) %>% summarize(accuracy=mean(accuracy)))
print(mean_df %>% filter(tpt==max(tpt)) %>% group_by(agent) %>% summarize(accuracy=mean(accuracy, na.rm=T)))

# Compute highest and lowest accuracy patterns
func_accuracy_df <- mean_df %>%
                group_by(agent, func.name) %>%
                summarize(accuracy=mean(accuracy), .groups="drop") %>%
                pivot_wider(names_from=agent, values_from=accuracy)
```

# Compute accuracy by age
```{r}
age_df <- df_kid %>%
          group_by(subj_id, func.name, tpt) %>%
          summarize(accuracy=mean(correct), age=mean(age), .groups="drop")

print(age_df %>% group_by(func.name, age) %>%
                 summarize(accuracy=mean(accuracy)), .groups="drop") %>%
                 group_by(age) %>%
                 summarize(accuracy=mean(accuracy))

print(age_df %>% filter(tpt==max(tpt)) %>% 
                 group_by(func.name, age) %>%
                 summarize(accuracy=mean(accuracy), .groups="drop") %>%
                 group_by(age) %>%
                 summarize(accuracy=mean(accuracy)))
```

# Estimate effect of age on accuracy
```{r}
exact_age_df <- df_kid %>%
                select(c(exact_age, age, subj_id, func.name, tpt, correct)) %>%
                mutate(exact_age_std = scale(exact_age)[,1],
                       tpt_std = scale(tpt)[,1],)

m <- glmer(correct ~ 1 + exact_age_std + tpt_std + (exact_age_std:tpt_std) + (1+tpt_std|func.name) + (1+tpt_std|subj_id),
           data=exact_age_df,
           family = binomial(link = "logit"), control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1000000)))

summary(m)
```

# Relationship between kid and adult accuracy
```{r}
df_comp <- bind_rows(df_adult, df_monkey_test, df_kid %>% mutate(agent=as.character(age))) %>%
           group_by(agent, subj_id, func.name) %>%
           summarize(accuracy=mean(correct, na.rm=T), .groups="drop") %>%
           group_by(agent, func.name) %>%
           summarize(accuracy=mean(accuracy, na.rm=T), .groups="drop") %>%
           pivot_wider(names_from="agent", values_from=accuracy) %>%
           na.omit()

for (x in 3:7) {
  print(paste0("age ", x))
  print(cor.test(df_comp$Adults, df_comp[[as.character(x)]], method="pearson"))
}

```


# Kids vs. Adults accuracy scatterplot
```{r, fig.width=15, fig.height=3.5}


df_path <- df_stim %>%
  rename(func.name = seq_id) %>%
  filter(tpt < 15) %>%
  group_by(func.name) %>%
  mutate(xmin = min(true_x, na.rm = TRUE),
         xmax = max(true_x, na.rm = TRUE),
         ymin = min(true_y, na.rm = TRUE),
         ymax = max(true_y, na.rm = TRUE),
         xmid = (xmin + xmax)/2,
         ymid = (ymin + ymax)/2,
         span = pmax(xmax - xmin, ymax - ymin),
         span = ifelse(span == 0, 1e-9, span),
         nx = (true_x - xmid) / span,
         ny = (true_y - ymid) / span) %>%
  ungroup() %>%
  select(func.name, tpt, nx, ny)


adult_acc <- df_adult %>%
  group_by(func.name, subj_id) %>%
  summarize(acc = mean(correct, na.rm = TRUE), .groups = "drop") %>%
  group_by(func.name) %>%
  summarize(mean_correct_adult = mean(acc, na.rm = TRUE), .groups = "drop")

kid_age_acc <- df_kid %>%
  group_by(age, func.name, subj_id) %>%
  summarize(acc = mean(correct, na.rm = TRUE), .groups = "drop") %>%
  group_by(age, func.name) %>%
  summarize(mean_correct_age = mean(acc, na.rm = TRUE), .groups = "drop")

age_comparison <- df_path %>%
  left_join(adult_acc, by = "func.name") %>%
  left_join(kid_age_acc, by = "func.name") %>%
  rename(age_year = age, age_accuracy = mean_correct_age) %>%
  filter(age_year %in% 3:7)

age_adult_correlations <- age_comparison %>%
  group_by(age_year) %>%
  summarize(r_adult = cor(age_accuracy, mean_correct_adult, use = "complete.obs"), .groups = "drop")

icon_size <- 0.08
age_labels <- function(x) paste(x, "year olds")

ggplot(data = age_comparison) +
  geom_abline() +
  geom_path(aes(x = age_accuracy + nx * icon_size,
                y = mean_correct_adult + ny * icon_size,
                group = func.name, color = func.name),
            alpha = 0.7, size = 0.4) +
  geom_point(aes(x = age_accuracy + nx * icon_size,
                 y = mean_correct_adult + ny * icon_size,
                 group = func.name, color = func.name),
             alpha = 0.8, size = 0.7) +
  geom_point(aes(x = age_accuracy + nx * icon_size,
                 y = mean_correct_adult + ny * icon_size,
                 group = func.name), color = "black",
             alpha = 0.05, size = 0.1) +
  facet_wrap(~age_year, nrow = 1, labeller = labeller(age_year = age_labels)) +
  geom_text(data = age_adult_correlations,
            aes(x = 0.87, y = 0.1,
                label = paste("italic(r) == ", sprintf("%.2f", r_adult))),
            size = 5, family = "Georgia", parse = TRUE) +
  labs(x = "Children Accuracy", y = "Adult Accuracy") +
  coord_cartesian(xlim = c(-0.02, 1.02), ylim = c(-0.02, 1.02)) +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  guides(color = "none") +
  paper_theme + theme(strip.background = element_blank())


```

# Humans (ages 3–7 and Adults) vs Monkeys scatter
```{r, fig.width=17, fig.height=3.5}

df_path_hm <- df_path

monkey_acc <- df_monkey_test %>%
  group_by(func.name, subj_id) %>%
  summarize(acc = mean(correct, na.rm = TRUE), .groups = "drop") %>%
  group_by(func.name) %>%
  summarize(mean_correct_monkey = mean(acc, na.rm = TRUE), .groups = "drop")

adult_acc <- df_adult %>%
  group_by(func.name, subj_id) %>%
  summarize(acc = mean(correct, na.rm = TRUE), .groups = "drop") %>%
  group_by(func.name) %>%
  summarize(mean_correct_adult = mean(acc, na.rm = TRUE), .groups = "drop")

kid_age_acc <- df_kid %>%
  group_by(age, func.name, subj_id) %>%
  summarize(acc = mean(correct, na.rm = TRUE), .groups = "drop") %>%
  group_by(age, func.name) %>%
  summarize(mean_correct_age = mean(acc, na.rm = TRUE), .groups = "drop")

# Assemble human groups: ages 3–7 and Adults
human_vs_monkey <- df_path_hm %>%
  left_join(monkey_acc, by = "func.name") %>%
  left_join(kid_age_acc, by = "func.name") %>%
  left_join(adult_acc, by = "func.name") %>%
  mutate(age_year = as.character(age),
         age_accuracy = mean_correct_age) %>%
  select(func.name, tpt, nx, ny, mean_correct_monkey, age_year, age_accuracy) %>%
  bind_rows(
    df_path_hm %>%
      left_join(monkey_acc, by = "func.name") %>%
      left_join(adult_acc, by = "func.name") %>%
      mutate(age_year = "Adult", age_accuracy = mean_correct_adult) %>%
      select(func.name, tpt, nx, ny, mean_correct_monkey, age_year, age_accuracy)
  ) %>%
  filter(age_year %in% c("3","4","5","6","7","Adult"))

# Per-facet correlations (Human vs Monkey)
human_correlations <- human_vs_monkey %>%
  distinct(func.name, age_year, mean_correct_monkey, age_accuracy) %>%
  group_by(age_year) %>%
  summarize(r_monkey = cor(age_accuracy, mean_correct_monkey, use = "complete.obs"), .groups = "drop")

icon_size <- 0.08
age_labels <- function(x) ifelse(x == "Adult", "Adults", paste(x, "year olds"))

ggplot(data = human_vs_monkey) +
  geom_abline() +
  geom_path(aes(x = age_accuracy + nx * icon_size,
                y = mean_correct_monkey + ny * icon_size,
                group = func.name, color = func.name),
            alpha = 0.7, size = 0.4) +
  geom_point(aes(x = age_accuracy + nx * icon_size,
                 y = mean_correct_monkey + ny * icon_size,
                 group = func.name, color = func.name),
             alpha = 0.8, size = 0.7) +
  geom_point(aes(x = age_accuracy + nx * icon_size,
                 y = mean_correct_monkey + ny * icon_size,
                 group = func.name), color = "black",
             alpha = 0.05, size = 0.1) +
  facet_wrap(~age_year, nrow = 1, labeller = labeller(age_year = age_labels)) +
  geom_text(data = human_correlations,
            aes(x = 0.12, y = 0.9,
                label = paste("italic(r) == ", sprintf("%.2f", r_monkey))),
            size = 5, family = "Georgia", parse = TRUE) +
  labs(x = "Human Accuracy", y = "Monkey Accuracy") +
  coord_cartesian(xlim = c(-0.02, 1.02), ylim = c(-0.02, 1.02)) +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  guides(color = "none") +
  paper_theme + theme(strip.background = element_blank(),
                      axis.title.x=element_text(size=22),
                      axis.title.y=element_text(size=21),
                      strip.text=element_text(size=19)) 

# ggsave("figs/human_vs_monkeys.png", dpi=400, width=17, height=3.5)
```






# Monkey test accuracy by individual
```{r}
mean_df <- df_monkey_test %>%
           group_by(func.name, tpt, subj_id) %>%
           summarize(accuracy=mean(correct, na.rm=T), .groups="drop")

print(mean_df %>% group_by(subj_id) %>% summarize(accuracy=mean(accuracy)))
print(mean_df %>% filter(tpt==max(tpt)) %>% group_by(subj_id) %>% summarize(accuracy=mean(accuracy, na.rm=T)))

# Highest and lowest accuracy patterns
func_accuracy_df <- mean_df %>% group_by(subj_id, func.name) %>% summarize(accuracy=mean(accuracy)) %>% pivot_wider(names_from=subj_id, values_from=accuracy)
```

# Relationship between monkeys
```{r}
print(cor.test(func_accuracy_df$"Monkey 1", func_accuracy_df$"Monkey 2", method="pearson"))
```

# Relationship between humans and monkeys
```{r}
df_comp <- bind_rows(df_adult, df_monkey_test, df_kid %>% mutate(agent=as.character(age))) %>%
           group_by(agent, subj_id, func.name) %>%
           summarize(accuracy=mean(correct, na.rm=T), .groups="drop") %>%
           group_by(agent, func.name) %>%
           summarize(accuracy=mean(accuracy, na.rm=T), .groups="drop") %>%
           pivot_wider(names_from="agent", values_from=accuracy) %>%
           na.omit()

print("Adults")
print(cor.test(df_comp$Monkeys, df_comp$Adults, method="pearson"))
for (x in 3:7) {
  print(paste0("age ", x))
  print(cor.test(df_comp$Monkeys, df_comp[[as.character(x)]], method="pearson"))
}

```

# Learning within patterns
```{r}
compute_fit <- function(df) {
  m <- glmer(
            correct ~ 1 +                          # fixed intercept
                      tpt_std +                    # fixed slope 
                      (1 + tpt_std | subj_id) +    # random intercept + slope for subject
                      (1 + tpt_std | func.name),   # random intercept + slope for function
            data = df,
            family = binomial(link = "logit")
  )
  return(m)
}

df_std <- df_all %>%
          mutate(agent = ifelse(agent=="Kids", paste0(age, " y/o"), agent)) %>%
          filter(tpt>2) %>%
          select(c("agent", "correct", "tpt", "func.name", "subj_id")) %>%
          mutate(tpt_std = scale(tpt)[,1])

for (agent_df in split(df_std, df_std$agent)) {
  print(unique(agent_df$agent))
  m <- compute_fit(agent_df)
  print(summary(m))
}

```

# Meta-learning in kids
```{r}
compute_fit <- function(df) {
  m <- glmer(
            correct ~ 1 +                          # fixed intercept
                      trial_idx_across_sessions_std + # fixed slope for sequence order
                      age_std +                    # fixed slope for age
                      tpt_std +                    # fixed slope for tpt
                      (age_std:tpt_std) +
                      (age_std:trial_idx_across_sessions_std) +
                      (tpt_std:trial_idx_across_sessions_std) +
                      (1 + tpt_std + trial_idx_across_sessions_std | subj_id) + # random intercept + slopes for subject
                      (1 + tpt_std | func.name),            # random intercept + slopes for function
            data = df,
            family = binomial(link = "logit"),
            control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
  )
  return(m)
}

df_std <- df_kid %>%
          select(c("agent", "exact_age", "correct", "tpt", "func.name", "subj_id", "session", "trial_idx", "trial_idx_across_sessions")) %>%
          mutate(tpt_std = scale(tpt)[,1],
                 trial_idx_std = scale(trial_idx)[,1],
                 session_std = scale(session)[,1],
                 trial_idx_across_sessions_std = scale(trial_idx_across_sessions)[,1],
                 age_std = scale(exact_age)[,1])

m <- compute_fit(df_std)
print(summary(m))

```

# Meta-learning in adults
```{r}
compute_fit <- function(df) {
  m <- glmer(
            correct ~ 1 +                          # fixed intercept
                      trial_idx_std +                  # fixed slope for sequence order
                      tpt_std +                    # fixed slope on tpt
                      (trial_idx_std:tpt_std) +
                      (1 + tpt_std + trial_idx_std | subj_id) + # random intercept + slopes for subject
                      (1 + tpt_std | func.name),            # random intercept + slopes for function
            data = df,
            family = binomial(link = "logit"),
            control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
  )
  return(m)
}

df_std <- df_adult %>%
          select(c("agent", "correct", "tpt", "func.name", "subj_id", "trial_idx")) %>%
          mutate(tpt_std = scale(tpt)[,1],
                 trial_idx_std = scale(trial_idx)[,1])

m <- compute_fit(df_std)
print(summary(m))

```


# Analogous analyses for inferred accuracy
#########################################

# Compute overall and final timepoint accuracy by agent 
```{r}
df_adult_modeled <- read.csv(paste0(preprocessed_data_dir, 'inferred_accuracy/mean_adults.csv')) %>%
                    mutate(agent="Adults") %>%
                    rename(subj_id = r_id)
df_kid_modeled <- read.csv(paste0(preprocessed_data_dir, 'inferred_accuracy/mean_kids.csv')) %>%
                  mutate(agent="Kids") %>%
                  rename(subj_id = r_id)
df_monkey_test_modeled <- read.csv(paste0(preprocessed_data_dir, 'inferred_accuracy/mean_monkeys.csv')) %>%
                     mutate(agent="Monkeys") %>%
                     rename(subj_id = r_id)
df_all_modeled <- bind_rows(df_adult_modeled, df_kid_modeled, df_monkey_test_modeled)
```
# Mean p_true
```{r}
mean_df <- df_all_modeled %>%
           group_by(agent, func.name, tpt, subj_id) %>%
           summarize(accuracy=mean(prob_true, na.rm=T), .groups="drop") %>%
           group_by(agent, func.name, tpt) %>%
           summarize(accuracy=mean(accuracy, na.rm=T))

print(mean_df %>% group_by(agent) %>%
                  summarize(accuracy = mean(accuracy)))
print(mean_df %>% filter(tpt==max(tpt)) %>%
                  group_by(agent) %>%
                  summarize(caccuracy=mean(accuracy, na.rm=T)))

# Compute highest and lowest accuracy patterns
func_accuracy_df <- mean_df %>%
                    group_by(agent, func.name) %>%
                    summarize(accuracy=mean(accuracy), .groups="drop") %>%
                    pivot_wider(names_from=agent, values_from=accuracy)
```
# Compute inferred accuracy by age
```{r}
age_df <- df_kid_modeled %>%
         group_by(age, func.name, tpt, subj_id) %>%
         summarize(accuracy=mean(prob_true, na.rm=T), .groups="drop") %>%
         group_by(age, func.name, tpt) %>%
         summarize(accuracy=mean(accuracy, na.rm=T))

print(age_df %>%
      group_by(func.name, age) %>%
      summarize(accuracy=mean(accuracy)), .groups="drop") %>%
      group_by(age) %>%
      summarize(accuracy=mean(accuracy))

print(age_df %>%
      filter(tpt==max(tpt)) %>% 
      group_by(func.name, age) %>%
      summarize(accuracy=mean(accuracy), .groups="drop") %>%
      group_by(age) %>%
      summarize(accuracy=mean(accuracy)))
```

# Relationship between kid and adult accuracy
```{r}
df_comp <- df_all_modeled %>%
           mutate(agent = ifelse(agent=="Kids", paste0(age, " y/o"), agent)) %>%
           group_by(agent, subj_id, func.name) %>%
           summarize(accuracy=mean(prob_true, na.rm=T), .groups="drop") %>%
           group_by(agent, func.name) %>%
           summarize(accuracy=mean(accuracy, na.rm=T), .groups="drop") %>%
           pivot_wider(names_from="agent", values_from=accuracy) %>%
           na.omit()

for (x in 3:7) {
  print(paste0("age ", x))
  print(cor.test(df_comp$Adults, df_comp[[paste0(x, " y/o")]], method="pearson"))
}

```

# Monkey accuracy by subj
```{r}
mean_df <- df_monkey_test_modeled %>%
           group_by(func.name, tpt, subj_id) %>%
           summarize(accuracy=mean(prob_true, na.rm=T), .groups="drop")

print(mean_df %>% group_by(subj_id) %>%
                  summarize(accuracy=mean(accuracy)))
print(mean_df %>% filter(tpt==max(tpt)) %>% 
                  group_by(subj_id) %>%
                  summarize(accuracy=mean(accuracy, na.rm=T)))

# Highest and lowest accuracy patterns
func_accuracy_df <- mean_df %>%
                    group_by(subj_id, func.name) %>%
                    summarize(accuracy=mean(accuracy)) %>%
                    pivot_wider(names_from=subj_id, values_from=accuracy)
```
# Relationship between monkeys
```{r}
print(cor.test(func_accuracy_df$"Monkey 1", func_accuracy_df$"Monkey 2", method="pearson"))
```

# Relationship between human and monkey inferred accuracy
```{r}
print("Adults")
print(cor.test(df_comp$Monkeys, df_comp$Adults, method="pearson"))
for (x in 3:7) {
  print(paste0("age ", x))
  print(cor.test(df_comp$Monkeys, df_comp[[paste0(x, " y/o")]], method="pearson"))
}

```

# 
######################################



